Effect of character correlation

### 2017-09-19 Analysis/EffectCorrelationFigure.Rmd
Renamed figure file

Results
-----------------------------------

@@

@@

Some stats
-----------------------------------

Supp
-----------------------------------

Plotting the results for 25 taxa

```{r, fig.width=12, fig.height=6}
## Comparisons to the best tree (RF)
plot.results.single(t25_list, metric = 2, what = "best",
    main = "comparison to 'best' tree (25 taxa)", legend = TRUE, NTS = TRUE)
```

```{r, fig.width=12, fig.height=6}
## Comparisons to the best tree (Triplets)
plot.results.single(t25_list, metric = 4, what = "best",
    main = "comparison to 'best' tree (25 taxa)", legend = TRUE, NTS = TRUE)
```

```{r, fig.width=12, fig.height=6}
## Comparisons to the null tree (RF)
plot.results.single(t25_list, metric = 2, what = "null",
    main = "comparison to 'null' tree (25 taxa)", legend = TRUE, NTS = TRUE)
```

```{r, fig.width=12, fig.height=6}
## Comparisons to the null tree (Triplets)
plot.results.single(t25_list, metric = 4, what = "null",
    main = "comparison to 'null' tree (25 taxa)", legend = TRUE, NTS = TRUE)
```

Plotting the results for 75 taxa

```{r, fig.width=12, fig.height=6}
## Comparisons to the best tree (RF)
plot.results.single(t75_list, metric = 2, what = "best",
    main = "comparison to 'best' tree (75 taxa)", legend = TRUE, NTS = TRUE)
```

```{r, fig.width=12, fig.height=6}
## Comparisons to the best tree (Triplets)
plot.results.single(t75_list, metric = 4, what = "best",
    main = "comparison to 'best' tree (75 taxa)", legend = TRUE, NTS = TRUE)
```

```{r, fig.width=12, fig.height=6}
## Comparisons to the null tree (RF)
plot.results.single(t75_list, metric = 2, what = "null",
    main = "comparison to 'null' tree (75 taxa)", legend = TRUE, NTS = TRUE)
```

```{r, fig.width=12, fig.height=6}
## Comparisons to the null tree (Triplets)
plot.results.single(t75_list, metric = 4, what = "null",
    main = "comparison to 'null' tree (75 taxa)", legend = TRUE, NTS = TRUE)
```

Plotting the results for 150 taxa

```{r, fig.width=12, fig.height=6}
## Comparisons to the best tree (RF)
plot.results.single(t150_list, metric = 2, what = "best",
    main = "comparison to 'best' tree (150 taxa)", legend = TRUE, NTS = TRUE)
```

```{r, fig.width=12, fig.height=6}
## Comparisons to the best tree (Triplets)
plot.results.single(t150_list, metric = 4, what = "best",
    main = "comparison to 'best' tree (150 taxa)", legend = TRUE, NTS = TRUE)
```

```{r, fig.width=12, fig.height=6}
## Comparisons to the null tree (RF)
plot.results.single(t150_list, metric = 2, what = "null",
    main = "comparison to 'null' tree (150 taxa)", legend = TRUE, NTS = TRUE)
```

```{r, fig.width=12, fig.height=6}
## Comparisons to the null tree (Triplets)
plot.results.single(t150_list, metric = 4, what = "null",
    main = "comparison to 'null' tree (150 taxa)", legend = TRUE, NTS = TRUE)
```

Checking the results for 25 taxa

@@

```{r, fig.width=12, fig.height=6}
## Checking comparisons (RF)
plot.results.single(t25_list, metric = 2, what = "check",
    main = "Check comparison (25 taxa)", legend = TRUE, NTS = TRUE)
```

```{r, fig.width=12, fig.height=6}
## Checking comparisons (Triplets)
plot.results.single(t25_list, metric = 4, what = "check",
    main = "Check comparison (25 taxa)", legend = TRUE, NTS = TRUE)
```

Checking the results for 75 taxa

@@

```{r, fig.width=12, fig.height=6}
## Checking comparisons (RF)
plot.results.single(t75_list, metric = 2, what = "check",
    main = "Check comparison (75 taxa)", legend = TRUE, NTS = TRUE)
```

```{r, fig.width=12, fig.height=6}
## Checking comparisons (Triplets)
plot.results.single(t75_list, metric = 4, what = "check",
    main = "Check comparison (75 taxa)", legend = TRUE, NTS = TRUE)
```

Checking the results for 150 taxa

@@

```{r, fig.width=12, fig.height=6}
## Checking comparisons (RF)
plot.results.single(t150_list, metric = 2, what = "check",
    main = "Check comparison (150 taxa)", legend = TRUE, NTS = TRUE)
```

```{r, fig.width=12, fig.height=6}
## Checking comparisons (Triplets)
plot.results.single(t150_list, metric = 4, what = "check",
    main = "Check comparison (150 taxa)", legend = TRUE, NTS = TRUE)
```

>>>>

# Results (plots)

@@

# Results supplementary

## Effect of character correlation compared to the null ("random") trees

@@

## Ability to recover the "true" tree

How different are the "normal" and "random" trees from the true trees

### 25 taxa

@@

### 75 taxa

@@

### 150 taxa

@@
